---
title: "A/B testing Using Customer Visits Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=T,comment="##",fig.height=5.5, fig.width=18,
dpi=2*72, warning=F, options(scipen=999), message = F)
options(dplyr.summarise.inform = FALSE)
```

# Libraries
```{r}
library(tidyverse)
library(powerMediation)
library("knitr")
```

```{r}
themeSajjad <-   
  theme(axis.text = element_text(size = 20), 
  axis.title = element_text(size = 17),
  legend.title=element_text(size=20),
  legend.text = element_text(size = 20),
  axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
```


# Read data
```{r}
z <- read_csv(paste0(here::here(), "/ab_data.csv"))
```

```{r}
x <- z
```

# Missing values

```{r}
nMiss <- function(x) sum(is.na(x))

x %>%
  summarise_all(nMiss)
```
No missing values.

# Exploring convertion rate across groups

```{r}
x %>%
  group_by(group) %>%
  summarise(n = n(), conversionRate = mean(converted))
```
There are `r nrow(x %>% filter(group == "control"))` users in the control group 
and `r nrow(x %>% filter(group == "treatment"))` users in the treatment group.

The average conversion rate for the is 
`r round(mean(x$converted[x$group == "control"]), 3)` for the control group and
`r round(mean(x$converted[x$group == "treatment"]), 3)` for the treatment group.


# A/B test (Checking effect of group on conversion rate)
We want to develop a Logistic Regression model to evaluate the effects of groups
assigned to users in their conversion rate. Before running the model we need to 
make sure we adjust the model for other factors that might have affected the 
rate of conversion. In the dataset we timestamp and landing_page that both could
potentially affect the conversion rate as different month could have different 
user interest rate and landing_pages are different and one cannot compare effect
of groups on conversion rate for differnt landing_page`s.

Let's first check how conversion rate changes in different landing pages.

```{r}
x %>%
  group_by(group, landing_page) %>%
  summarise(m = mean(converted)) %>%
  ggplot(aes(x = group, y = m, fill = group))+
  geom_bar(stat = "identity")+
  labs(x = "Group", y = "Landing Page")+
  scale_fill_brewer(palette = "Set1")+
  coord_flip()+
  themeSajjad+
  facet_grid(~landing_page)+
  theme(strip.text.x = element_text(size = 20, colour = "red", angle = 0))
```

And now check how conversion rate changes through time. For simplicty I only
consider effect of date and will remove time of the day from the datetime 
object. 
```{r}
x <- x %>%
  mutate(date = as.Date(format(timestamp, "%Y-%m-%d"), "%Y-%m-%d" ))
```

```{r}
x %>%
  group_by(date) %>%
  mutate(n = sum(converted)) %>%
  ggplot(aes(x = date, y = n))+
  geom_line(stat = "identity")+
  scale_x_date(date_labels = "%b %d", date_breaks = "1 day")
```

It looks like the 2nd and 24th days of January had lower conversion 
rates. Let's check the datbase for these two days only to see if there's any
differences between the to groups in that those days.
```{r}
x %>%
  filter(date %in% c(as.Date("2017-01-02", "%Y-%m-%d"), 
                     as.Date("2017-01-24", "%Y-%m-%d"))) %>%
  group_by(group) %>%
  summarise(m = mean(converted))
```

The average conversion rate for those two days are similar to the rest of the 
dataset, so we can assume the conversion rate has been the same across the study
period and do not include date in the model.

Let's now build our Logistic Regression model which only inclues group and 
landing_page variables. Here's our hypothesis for this test:

$H_{0}: P_{control} = P_{treatment}$
$H_{a}: P_{control} < P_{treatment}$
```{r}
x <- x %>% mutate(converted = factor(converted, levels = c(0, 1)))
lrModel <- glm(converted ~ group + landing_page, data = x, family = "binomial")

summary(lrModel)
```

Looking at the p values of the model, we don't have sufficient evidence to reject
the null hypothesis. In the context of our test, this means that there is not 
enough statistical evidence in our survey to show a difference in the rate of 
conversion between two different groups, when adjusted for landing page.
